---
title: "R Notebook"
output: html_notebook
---

# Load Libraries and Data
```{r}
library(tidyverse)
library(tidymodels)
library(palmerpenguins)
```

```{r}
penguins_df <- penguins %>% drop_na()
penguins_df
```

# Plot Bar Plot of Body Mass

```{r}
# group_by species and summarize mean_body_mass
penguins_df %>%
  group_by(species) %>%
  summarize(mean_body_mass = mean(body_mass_g)) %>%
  ggplot() +
    geom_bar(mapping = aes(y = species, x = mean_body_mass), stat = "identity")

```
Are Chinstrap Penguins bigger than Adelie Penguins?

# Calculate Confidence Interval

The lazy interpretation: We are 95 percent confident that the 95 percent confidence interval contains the true population mean.
[Statistical Inference via Data Science: A ModernDive into R and the Tidyverse! ](https://moderndive.com/8-confidence-intervals.html#shorthand), Chester Ismay and Albert Y. Kim 

A more precise interpretation:
"If multiple samples were drawn from the same population and a 95% CI calculated for each sample, we would expect the population mean to be found within 95% of these CIs." 
[How do I interpret a confidence interval?](https://pubmed.ncbi.nlm.nih.gov/27184382/), Sheila F O'Brien and Qi Long Yi

## "Theoretical Way"
[equation](https://www.google.com/search?client=safari&rls=en&q=confidence+interval+equation&ie=UTF-8&oe=UTF-8)
```{r}
# group_by species
# summarize mean, std, and n
# mutate se, lower nd upper ci
# se_body_mass = std_body_mass / sqrt(n)
# lower_ci = mean_body_mass + qt(0.025, n - 1) * se_body_mass
# upper_ci = mean_body_mass + qt(0.975, n - 1) * se_body_mass

penguins_ci <- penguins_df %>%
  group_by(species) %>%
  summarize(
    mean_body_mass = mean(body_mass_g),
    std_body_mass = sd(body_mass_g),
    n_penguins = n()
  ) %>%
  mutate(
    se_body_mass = std_body_mass / sqrt(n_penguins),
    lower_ci = mean_body_mass - qt(0.975, n_penguins - 1) * se_body_mass,
    upper_ci = mean_body_mass + qt(0.975, n_penguins - 1) * se_body_mass
  )

penguins_ci
```
## Simulation Way (Bootstrapping)
Bootstrapping
- Assume sample is representative of population
- Resample with replacement from sample (Sample pulling itself up by the bootstraps!)

```{r}
# Use filter to get a specific penguin
# Use specify to focus on body_mass_g
# Use generate to generate 100 reps (bootstrap)
# Use calculate to calculate the "mean"
# use get_confidence_interval(level = 0.95, type = "se", point_estimate = 3706.164)
penguins_df %>%
  filter(species == "Adelie") %>%
  specify(response = body_mass_g) %>%
  generate(reps = 300, method = "bootstrap") %>%
  calculate(stat = "mean") %>%
  get_confidence_interval(level = 0.95, type = "se", point_estimate = 3706.164)

```

```{r}
penguins_df %>%
  filter(species == "Chinstrap") %>%
  specify(response = body_mass_g) %>%
  generate(reps = 300, method = "bootstrap") %>%
  calculate(stat = "mean") %>%
  get_confidence_interval(level = 0.95, type = "se", point_estimate = 3733.088)
```

```{r}
penguins_df %>%
  filter(species == "Gentoo") %>%
  specify(response = body_mass_g) %>%
  generate(reps = 300, method = "bootstrap") %>%
  calculate(stat = "mean") %>%
  get_confidence_interval(level = 0.95, type = "se", point_estimate = 5092.437)
```


```{r}
penguins_df %>%
  filter(species == "Adelie") %>%
  specify(response = body_mass_g) %>%
  generate(reps = 2000, method = "bootstrap") %>%
  calculate(stat = "mean") %>%
  ggplot() +
    geom_histogram(aes(x = stat))
```
```


# Add Confidence Interval to Bar Plot
```{r}
penguins_df %>%
  group_by(species) %>%
  summarize(mean_body_mass = mean(body_mass_g)) %>%
  ggplot() +
    geom_bar(mapping = aes(y = species, x = mean_body_mass), stat = "identity") +
    geom_errorbar(data=penguins_ci, mapping = aes(y = species, xmin = lower_ci, xmax = upper_ci))
```



# Plot Confidence Intervals on Jitter

## Plot Jitter
```{r}
penguins_df %>%
  ggplot() +
    geom_jitter(aes(y = species, x = body_mass_g, color = species)) + 
    geom_errorbar(data=penguins_ci, mapping = aes(y = species, xmin = lower_ci, xmax = upper_ci)) +
    geom_point(data=penguins_ci, mapping = aes(y = species, x = mean_body_mass))
```


## Add Confidence Interval to Jitter Plot

```{r}
# user geom_errorbar and geom_point (for mean)
body_mass_jitter + 
  geom_errorbar(data = body_mass_ci, aes(y = species, xmin = lower_ci, xmax = upper_ci)) + 
  geom_point(data = body_mass_se, aes(y = species, x = mean_body_mass))
```


# Plot Confidence Interval on Violin Plot
```{r}

penguins_violin <- penguins_df %>%
  ggplot() +
    geom_violin(aes(y = species, x = body_mass_g))
    
penguins_violin
```

```{r}
penguins_violin +
  geom_errorbar(data = body_mass_ci, aes(y = species, xmin = lower_ci, xmax = upper_ci)) + 
  geom_point(data = body_mass_se, aes(y = species, x = mean_body_mass))
```